Artificial Intelligence for the Automated Synthesis and Validation of Programs

### 2018-06-10 doc/programming-project/AI-programming.tex
project reference added

Since 2016 Diego is holding a four-year FPU grant on {\em Causal discovery for predictive analysis} (FPU16/03184). Diego is also involved on the current research project of the GPRS from the Spanish national research plan on {\em activity recognition}.

@@

On the other hand, {\em program validation} is the task of proving, or disproving, the correctness of a given program with respect to a certain formal specification or property. Program validation is considered a necessary step for program synthesis.

Closely related to {\em program validation} are the aims of {\em model checking}~\cite{clarke1999model}. In model checking a given model of a system, is exhaustively and automatically checked to verify  whether this model meets a given specification. Typically the specification contains safety requirements such as the absence of deadlocks and similar critical states that can cause the system to crash. Both the model of the system and the specification are formulated in a formal language. To this end, the problem is formulated as a task in logic, namely to check whether a given structure satisfies a given logical formula.

>>>>

Since 2016 Diego is holding a four-year FPU grant on {\em Causal discovery for predictive analysis} (FPU16/03184). Diego is also involved on the current research project TIN2017-88476-C2-1-R of the GPRS from the Spanish national research plan with title {\small\em RECONOCIMIENTO DE ACTIVIDADES Y PLANIFICACION AUTOMATICA PARA EL DISEÑO DE ASISTENTES INTELIGENTES}.

@@

On the other hand, {\em program validation} is the task of proving, or disproving, the correctness of a given program with respect to a certain formal specification or property. Program validation is considered a necessary step for program synthesis. {\em Model checking} is the best-known approach for program validation~\cite{clarke1999model}. In model checking a given model of a system, is exhaustively and automatically checked to verify  whether this model meets a given specification. Typically the specification contains safety requirements such as the absence of deadlocks and similar critical states that can cause the system to crash. Both the model of the system and the specification are formulated in a formal language. To this end, the problem is formulated as a task in logic, namely to check whether a given structure satisfies a given logical formula.
